### 2021-07-08 paper/paper.tex
taking Joe's advice

\begin{abstract}
Combinatorial interaction testing is an automated way to generate test cases for unit tests. It's designed to be the best guess at the fewest unit tests that will give good decision coverage. This article discusses when to use this technique and how to apply it with the \utd package in the Julia testing ecosystem. This article offers a general approach to using automated test generation for different software testing applications.
\end{abstract}

@@

\vskip 6pt
The first unit tests for a new library often derive from mimicking how a user might write client code. These happy-path tests are narrative. We may add tests that are our best guesses for corner cases of a function under test, but these are all considered manual testing.

@@

Here, the \verb|all_pairs| function is a combinatorial interaction test (\cit) design that uses the sample argument values to create a set of 16~test cases. It's a simple algorithm, with inputs that are easy to specify and use within an existing unit testing framework. The name, all-pairs, means that, if we look at the test cases, and we pick any two arguments, then pick any two values those arguments can take, there will be at least one test case that includes that pair of arguments.
\begin{lstlisting}[language=Julia]
julia> test_cases
16-element Vector{Vector{Any}}:
 [1, :a, naive, "none", 0.0]
 [4, :a, keyfitz, "RK4", 9.3]
 [8, :a, greville, "quadrature", -1.2]
 [1, :a, monotonic, "QUADPACK", Inf]
 [1, :b, naive, "RK4", -1.2]
 [8, :b, keyfitz, "none", Inf]
 [4, :b, greville, "QUADPACK", 0.0]
 [1, :b, monotonic, "quadrature", 9.3]
 [4, :c, naive, "quadrature", Inf]
 [1, :c, keyfitz, "QUADPACK", -1.2]
 [8, :c, greville, "none", 9.3]
 [8, :c, monotonic, "RK4", 0.0]
 [8, :d, naive, "QUADPACK", 9.3]
 [1, :d, keyfitz, "quadrature", 0.0]
 [1, :d, greville, "RK4", Inf]
 [4, :d, monotonic, "none", -1.2]
 \end{lstlisting}
In this article, we describe when to use \cit and how to use \cit within the Julia language's unit testing ecosystem.

@@

Most of the techniques for automatic test case generation focus more on making a smart set of tests than they focus on making few tests that are of high quality. \cit generates fewer tests that are designed to give good branch coverage~\cite{Nie2011-yl,Grindal2005-su,Kuhn2010-ak}.

@@

\vskip 6pt
The \cit in \utd takes the time to optimize the choice of test cases so that they can test the code well. The theory of the game is that each if--then in the code will branch depending on interacting combinations of argument values, so \cit ensures all combinations of $n$ arguments are tried in at least one test case. Here, $n=2$ for two-way testing, also known as all-pairs testing~\cite{pairwise-website}, but studies have shown that wayness up to $n=6$ can be useful~\cite{Petke2015-ex}.

@@

\begin{unnumlist}
\item Integration test of modules, where a module \textsc{api} produces many possible ways to call it.
\item User-level tests of an application, where there are choices in dialog boxes, parameter files, and command-line options.
\item Systems outside of Julia, such as the problem of hardware integration.
\end{unnumlist}

@@

\vskip 6pt
An \emph{equivalence class} is a set of input values that would discover the same faults in the code. For instance, if a given function fails for \verb|arg3<2.7|, then it will fail for \verb|arg3=2| as well as \verb|arg3=2.5|, so we consider those equivalent with respect to finding faults. Our goal, as authors of unit tests, is to select argument values that represent equivalence classes for the function under test. There isn't a lot of guidance on how to choose these values. You can guess them by looking at the code or by looking at a specification for the function.

\vskip 6pt
One way to defend against our uncertainty about equivalence classes is to combine combinatorial test generation with random testing. Decide that each argument value represents an equivalence class. Then generate test cases, but use the values in those test cases to sample randomly from the partitions. This is one way to introduce bias, and control, into random test selection. It points to treating test case generation as a continuum of techniques.

@@

\begin{lstlisting}[language=Julia]
rng = Random.MersenneTwister(9790242)
slow_and_short = all_pairs(parameters...; engine = GND(rng = rng, M = 50))
\end{lstlisting}

@@

\vskip 6pt
It helps to consider the check for failure, not as \verb|result == oracle(test_case...)| but as a rule that takes both result and test case into account. For instance, some mathematical calculations solve inverse problems, so that the result can be fed into a related forward problem. The test becomes whether it can recover its input values.

\vskip 6pt
Automated testing of results often takes the form of testing for traits of the result, not exact values. For example, you could test a function for continuity of outputs near the given input. You could use statistical measures, such as maximum absolute error, to assert that a function's output is near some standard result. There is a powerful technique to assert symmetries in function arguments. For instance if, for some function under test, $f$, a symmetry test might check that \verb|f(a, b)=f(2*a, b/2)|~\cite{Segura2016-qh}.

@@

\vskip 6pt
The \utd package expanded on the implementation of two $n$-way combinatorial interaction testing algorithms. One is the greedy, non-deterministic algorithm known as \textsc{aetg}~\cite{Cohen1997-lb}. The other is a deterministic, parameter-choosing algorithm called \textsc{ipo-g}~\cite{Lei2008-xt}. Like many greedy algorithms, these can be sensitive to small, sometimes unspecified, choices in implementation. We used two approaches for this package in order to make algorithms that had the right features and performed well.

@@

\vskip 6pt
For example, there is a common moment in these algorithms where a putative test case, partially specified, is matched against a coverage tuple, which will have $n$ specified argument values for $n$-way coverage. Given just one argument from the test case and one argument from the tuple, there are five ways they can compare.
\begin{center}
\begin{tabular}{rll}
comparison & test case & tuple \\ \hline
ignores & * & * \\
skips & $a$ & * \\
misses & * & $b$ \\
matches & $a$ & $b=a$ \\
mismatches & $a$ & $b\ne a$
\end{tabular}
\end{center}
Only the last comparison is clearly a mismatch. If we compare multiple arguments of the test case and tuple, we can quantify that comparison as having zero or more ``ignores,'' zero or more ``skips,'' and so-on. This means there are $2^4-1$ ways that a non-zero test case and tuple can compare, even if they have no mismatches.

\vskip 6pt
The \textsc{ipo-g} algorithm matches tuples in two places, once when it expands the number of columns of test cases and once when it fills in values at the end. In both cases, after testing $15\times 15$ ways of matching, we found that the simple requirement that there be no mismatches performed as well as any other choice, while more complicated matching strategies resulted in significantly more test cases for the same coverage.

@@

\vskip 6pt
Property-based testing offers domain-specific ways to describe the domain of each argument, or sets of arguments, so that the test author can focus on the domain of the function instead of the exact test suite. Tools of this kind can watch for failed tests, and then they can simplify the test arguments while checking for failure, in order to find the simplest test that fails. This is extraordinarily useful for fault-finding but, again, will use more testing resources~\cite{loscher2018automating}.

>>>>

\begin{abstract}
Combinatorial interaction testing is an automated way to generate test cases for unit tests. It's designed to be a best guess at the fewest unit tests that will give good decision coverage. This article discusses when to use this technique, a general approach to using automated test generation for different software testing applications, and, in particular, how to apply it with the \utd package in the Julia testing ecosystem.
\end{abstract}

@@

\vskip 6pt
The first unit tests for a new library often derive from mimicking how a user might write client code. These happy-path tests are narrative. We may add tests for corner cases of a function under test, but these may be limited by imagination and available effort.

@@

Here, the \verb|all_pairs| function is a combinatorial interaction test (\cit) design that uses the sample argument values to choose a set of 16~test cases out of a total possible 768~test cases. The inputs are easy to specify and use within an existing unit testing framework. The name, all-pairs, means that, if we look at the test cases, and we pick any two arguments, then pick any two values those arguments can take, there will be at least one test case that includes that pair of arguments.
\begin{lstlisting}[language=Julia]
julia> test_cases
16-element Vector{Vector{Any}}:
 [1, :a, naive, "none", 0.0]
 [4, :a, keyfitz, "RK4", 9.3]
 [8, :a, greville, "quadrature", -1.2]
 [1, :a, monotonic, "QUADPACK", Inf]
 [1, :b, naive, "RK4", -1.2]
 [8, :b, keyfitz, "none", Inf]
 [4, :b, greville, "QUADPACK", 0.0]
 [1, :b, monotonic, "quadrature", 9.3]
 [4, :c, naive, "quadrature", Inf]
 [1, :c, keyfitz, "QUADPACK", -1.2]
 [8, :c, greville, "none", 9.3]
 [8, :c, monotonic, "RK4", 0.0]
 [8, :d, naive, "QUADPACK", 9.3]
 [1, :d, keyfitz, "quadrature", 0.0]
 [1, :d, greville, "RK4", Inf]
 [4, :d, monotonic, "none", -1.2]
 \end{lstlisting}
In this article, we describe when to use \cit and how to use \cit within the Julia language's unit testing ecosystem.

@@

Compared to other techniques for automatic test case generation, \cit generates fewer tests, choosing them in a way designed to give good branch coverage~\cite{Nie2011-yl,Grindal2005-su,Kuhn2010-ak}.

@@

\vskip 6pt
The \cit in \utd takes the time to optimize the choice of test cases so that they can test the code well. The assumption is that each if--then in the code will branch depending on interacting combinations of argument values, so \cit ensures all combinations of $n$ arguments are tried in at least one test case. Here, $n=2$ for two-way testing, also known as all-pairs testing~\cite{pairwise-website}, but studies have shown that wayness up to $n=6$ can be useful~\cite{Petke2015-ex}.

@@

\begin{itemize}
\item Integration test of modules, where a module \textsc{api} produces many possible ways to call it.
\item User-level tests of an application, where there are choices in dialog boxes, parameter files, and command-line options.
\item Systems outside of Julia, such as the problem of hardware integration.
\end{itemize}

@@

\vskip 6pt
An \emph{equivalence class} is a set of input values that would discover the same faults in the code. For instance, if a given function fails for \verb|arg3<2.7|, then it will fail for \verb|arg3=2| as well as \verb|arg3=2.5|, so we consider those equivalent with respect to finding faults. As authors of unit tests, we select argument values that represent equivalence classes for the function under test. You can choose them by looking at the code or by looking at a specification for the function, but it's possible to miss an equivalence class and miss the faults discovered by that equivalence class.

\vskip 6pt
One way to defend against our uncertainty about equivalence classes is to combine combinatorial test generation with random testing. Decide that each argument value in the \cit specification represents a generator of values from an equivalence class. Then each test case, output from \cit, is a list of random argument generators. This introduces bias, and control, into random test selection. It points to treating test case generation as a continuum of techniques.

@@

\begin{lstlisting}[language=Julia]
rng = Random.MersenneTwister(9790375)
slow_and_short = all_pairs(parameters...; engine = GND(rng = rng, M = 50))
\end{lstlisting}

@@

\vskip 6pt
It helps to consider the check for failure, not as an assertion about the result,
\begin{lstlisting}[language=Julia]
@assert result == oracle(test_case...)
\end{lstlisting}
but as a rule that takes both result and test case into account.
\begin{lstlisting}[language=Julia]
@assert invariant(result, test_case...)
\end{lstlisting}
For instance, some mathematical calculations solve inverse problems, so that the result can be fed into a related forward problem. The test becomes whether it can recover its input values. Another test would be whether nearby inputs give continuous outputs. Lastly, a technique to assert symmetries in function arguments, when such symmetries exist in the function under test, has been shown to find faults~\cite{Segura2016-qh}. For instance, for some function under test, $f$, a symmetry test might check that \verb|f(a, b)=f(2*a, b/2)|.

@@

\vskip 6pt
The \utd package expands on the implementation of two $n$-way combinatorial interaction testing algorithms. One is the greedy, non-deterministic algorithm known as \textsc{aetg}~\cite{Cohen1997-lb}. The other is a deterministic, parameter-choosing algorithm called \textsc{ipo-g}~\cite{Lei2008-xt}. Like many greedy algorithms, these can be sensitive to small, sometimes unspecified, choices in implementation. We used two approaches for this package in order to make algorithms that had the right features and performed well.

@@

\vskip 6pt
For example, there is a common moment in these algorithms where a putative test case, partially specified, is matched against a coverage tuple, which will have $n$ specified argument values for $n$-way coverage. Given just one argument from the test case and one argument from the tuple, there are five ways they can compare.
\begin{center}
\begin{tabular}{rll}
comparison & test case & tuple \\ \hline
ignores & * & * \\
skips & $a$ & * \\
misses & * & $b$ \\
matches & $a$ & $b=a$ \\
mismatches & $a$ & $b\ne a$
\end{tabular}
\end{center}
Only the last comparison is clearly a mismatch. If we compare multiple arguments of the test case and tuple, we can quantify that comparison as having zero or more ``ignores,'' zero or more ``skips,'' and so-on. This means there are $2^4-1$ ways that a non-zero test case and tuple can compare, even if they have no mismatches. The \utd library has tuned its search for test cases by optimizing across these matching algorithms.

@@

\vskip 6pt
Property-based testing offers a specification to describe the domain of each argument, or sets of arguments, so that the test author can focus on the domain of the function instead of the exact test suite. Tools of this kind can watch for failed tests, and then they can simplify the test arguments while checking for failure, in order to find the simplest test that fails. This is extraordinarily useful for fault-finding but, again, will use more testing resources~\cite{loscher2018automating}.
